### 2022-11-30 paper4.tex
ie and eg

Consider a null hypothesis $H_0$ with prior probability $\pi=\P(H_0)$, so
$\P(H_1) =1-\pi$ is the prior probability of the alternative hypothesis $H_1$.
Computation of the posterior probability of $H_1$ is routine with Bayes'
theorem:
\begin{equation*}
  \Pr(H_{1} \given \data) = \frac{\Pr(\data \given H_{1}) \Pr(H_{1})}{\Pr(\data \given H_{0}) \Pr(H_{0}) +
    \Pr(\data \given H_{1}) \Pr(H_{1})}.
\end{equation*}
Bayes' theorem can be written in more compact form as
\begin{equation}\label{eq4:eq0}
  \frac{\Pr(H_{1} \given \data)}{\Pr(H_{0} \given \data)} =
  \frac{\Pr(\data \given H_{1})}{\Pr(\data \given H_{0})} \,  \frac{\Pr(H_{1})}{\Pr(H_{0})},
\end{equation}
\ie the posterior odds are the likelihood ratio times the prior odds. The
standard 'forward-Bayes' approach thus fixes the prior odds (or one of the
underlying probabilities), determines the likelihood ratio for the available
data, and takes the product to compute the posterior odds. Of course, the latter
can be easily back-transformed to the posterior probability
$\Pr(H_{1} \given \data)$, if required. The Problem of Priors is now apparent:
in order for us to update the odds in favour of $H_1$, we must first specify the
prior odds. This can be problematic in situations where, for example, the
evidence on which to base the prior odds is controversial or even non-existent.

@@

Forward-Bayesian updating tells us how to compute the posterior precision and
mean:
\begin{align}
\label{eq4:posterior-precision}
\delta' &= \delta + \kappa, \\
\mu' &= \frac{\mu \delta + x \kappa}{\delta'}.\label{eq4:posterior-mean}
\end{align}
For example, fixed-effect (FE) meta-analysis is based on iteratively applying
\eqref{eq4:posterior-precision} and \eqref{eq4:posterior-mean} to the summary
effect estimate $x_i$ with standard error $\sigma_i$ from the $i$-th study,
$i=1,\ldots,n$, starting with an initial precision of zero. Reverse-Bayes simply
inverts these equations, which leads to the following:
\begin{align}
\label{eq4:prior-precision}
\delta &= \delta' - \kappa,  \\
\mu &= \frac{\mu'\delta' - x \kappa}{\delta}, \label{eq4:prior-mean}
\end{align}
provided $\delta' > \kappa$, \ie the posterior precision must be larger than the
observational precision.

@@

\subsubsection{Challenging statistically non-significant findings}
\label{sec4:nonSigAnCred}
It is also possible to challenge ``non-significant'' findings (\ie those for
which the CI now includes zero, so $z^2 < z_{\alpha/2}^2$) using a prior that
pushes the posterior towards being credible in the Bayesian sense, with
posterior credible interval no longer including zero, corresponding to no
effect.

@@

For illustration we consider the data from the REMAP-CAP trial that supported
the RECOVERY trial finding of decreased COVID-19 mortality from corticosteroid
use. However, this trial involved far fewer patients, and despite the point
estimate showing efficacy, the relatively large uncertainty rendered the overall
finding non-significant at the 5\% level ($\hat{\theta} = -0.34$ [95\% CI
$-0.96$ to $0.29$]). Such an outcome is frequently (and wrongly) taken to imply
no effect. The use of AnCred leads to a more nuanced conclusion. The advocacy
limit AL on the log odds ratio scale for REMAP-CAP is $-1.89$, \ie $0.15$ on the
odds ratio scale, see also the right plot in Figure \ref{fig4:anCredEx}. Thus
advocates of the effectiveness of corticosteroids can regard the trial as
providing credible evidence of effectiveness despite its non-significance if
external evidence supports mortality reductions (in terms of odds) in the range
0\% to 85\%. So broad an advocacy range reflects the fact that this relatively
small trial provides only modest evidential weight, and thus little constraint
on prior beliefs about the effectiveness of corticosteroids.

@@

As before, while the large study approximation may be justified in
epidemiological examples, this is less likely to be true for RCTs. In such
cases, we can adapt the approach used for sceptical priors, the size and
composition of the advocacy prior being found by setting the numbers of events
$m$ in each arm the same, but this time allowing for different numbers of
non-events in each arm via the allocation ratio $K$. The resulting variance is
then
\begin{align*}
  \tau^{2} = \frac{2}{m} + \frac{K + 1}{n}
\end{align*}
where $n$ is the number of non-events in the arm used to support the null
hypothesis (\eg the control arm in an RCT). With the control arm event rate
$R = m/(m + n)$ constrained to match that of the actual study, we find
\begin{eqnarray*}
  m = \frac{2 - R(1 - K)}{\tau^{2}(1 - R)} & \mbox{ and }
  &n = \frac{m(1 - R)}{R}.
\end{eqnarray*}

@@

The Problem of Priors is at its most challenging in the context of entirely
novel ``out of the blue'' effects for which no obviously relevant external
evidence exist. By their nature, such findings often attract considerable
interest both within and beyond the research community, making their reliability
of particular importance. Given the absence of external sources of evidence,
\citet{Matthews2018} proposed the concept of \emph{intrinsic
  credibility}. This requires that the evidential weight of an unprecedented
finding is sufficient to put it in conflict with the sceptical prior rendering
it non-credible. In the AnCred framework, this implies a finding possesses
intrinsic credibility at level $\alpha$ if the estimate $\hat{\theta}$ is
outside the corresponding sceptical prior interval $[-\SL, \SL]$ extracted using
Reverse-Bayes from the finding itself, \ie $\hat{\theta}^2 > \SL^2$ with $\SL$
given in \eqref{eq4:S}. Matthews showed this implies an unprecedented finding is
intrinsically credible at level $\alpha=0.05$ if its $p$-value does not exceed
0.013.

@@

As an example, the $p$-value for intrinsic credibility for the RECOVERY trial
finding (with $p$-value $p=0.0002$) cited earlier is $\pIC = 0.01$ and thus the
probability of the replication effect going in the same direction (\ie reduced
mortality in this case) is $0.995$. In contrast, the finding from the smaller
REMAP-CAP trial (with $p=0.29$) leads to $\pIC = 0.46$, and the probability of
effect direction replication is hence only $0.77$.

@@

The plausibility of the sufficiently sceptical prior can be evaluated in light
of external evidence, but what should we do in the absence of such? We could
again use the \citet{Box1980} prior-predictive check as in
Section~\ref{sec4:IC}, however, the resulting tail probability is difficult to
compare to the Bayes-factor cut-off $\gamma$. When a specific alternative model
to the null is in mind, \citet[p. 391]{Box1980} also suggested to use a Bayes
factor for model criticism of the null model. Following this approach,
\citet{Pawel2020b} proposed to define a second Bayes factor contrasting the
sufficiently sceptical prior to an optimistic prior, which they defined as
$\theta \given H_2 \sim \Nor(\hat{\theta}, \sigma^2)$ the posterior of $\theta$
based on the data and the reference prior $f(\theta) \propto 1$. The optimistic
prior therefore represents the position of a proponent who takes the original
claim at face value. This leads to the second Bayes factor being
\begin{align}
  \label{eq4:bf12}
  \BF_{12} = \sqrt{\frac{2}{1 + g}} \cdot \exp\left\{-\frac{1}{2}\cdot \frac{z^{2}}{1 + g}\right\}.
\end{align}
Analogously to the tail probability approach from Section~\ref{sec4:IC},
intrinsic credibility is established if the data support the optimistic over the
sceptical prior at a higher level than they support the sceptical prior over the
null hypothesis, \ie if
\begin{align*}
  \BF_{12} \leq \BF_{01}
\end{align*}
with sufficiently sceptical relative prior variance $g$ from~\eqref{ggamma} used
in both Bayes factors. For example, if we challenge the RECOVERY trial finding
such that the resulting Bayes factor is only $\BF_{01} = 1/10$, we obtain
with~\eqref{eq4:sspv} the sufficiently sceptical relative prior variance
$g = 0.59$ and in turn with~\eqref{eq4:bf12} the Bayes factor $\BF_{12} = 1/64$,
so the finding is intrinsically credible at $\gamma = 1/10$.

@@

The right plot in Figure \ref{fig4:bf} illustrates application of the procedure
on data from the meta-analysis on association between COVID-19 mortality and
corticosteroids. The coefficient of variation of the advocacy prior is fixed to
$\text{CV} = 1/z(\gamma=1/3) = 0.67$ (for comparison, the CV of the advocacy
prior in traditional AnCred at $\alpha = 0.05$ is
$\text{CV} = 1/z_{\alpha/2}= 0.51$) and thus the Bayes factor $\BF_{01}$ only
depends on the relative mean $f = \mu/\hat{\theta}$. Under the sceptical prior
only the RECOVERY finding could be challenged at $\gamma = 1/3$ (where
$z(\gamma)=1.5$ corresponds to $\alpha=13$\%). With the advocacy prior this is
now also possible for the CAPE COVID finding \citep{Dequin2020}, where a prior
with mean $\mu = f \cdot \hat{\theta} = 0.37 \cdot (-0.79) = -0.29$ and standard
deviation $\tau = \text{CV} \cdot \mu = 0.2$ is able to make the finding
compelling at $\gamma = 1/3$. The corresponding prior credible interval for the
OR at level $1-\alpha$ ranges from 0.55 to 1, so advocates may still consider
the ``non-compelling'' finding as providing moderate evidence in favour of a
benefit, if external evidence supports mortality reductions in that range. Using
the prior-to-data conversion described in
Section~\ref{sec4:prior-data-translation}, the prior can be translated to a
trial with 69 events in both arms, but 206 non-events in the treatment and 182
non-events in the control arm (such that the mortality rate in the control arm
is the same as in the CAPE-COVID trial). Note that the advocacy prior may not be
unique, \eg for the CAPE COVID finding the prior with relative mean
$f^\prime = 1.26$ and standard deviation $\tau^\prime = 0.67$ also renders the
data as just compelling at $\gamma = 1/3$. We recommend to choose the prior with
$f$ closer to zero, as it is the more conservative choice.

@@

Application of the Analysis of Credibility with Bayes factors as described in
Section \ref{sec4:bfs} assumes some familiarity with Bayes factors as measures
of evidence. \citet{Colquhoun2019} argued that very few nonprofessional users of
statistics are familiar with the notion of Bayes factors or likelihood ratios.
He proposes to quantify evidence with the \emph{false positive risk}, ``if only
because that is what most users still think, mistakenly, that that is what the
$p$-value tells them''. More specifically, \citet{Colquhoun2019} defines the
\FPR{} as the posterior probability that the point null hypothesis $H_0$ of no
effect is true given the observed $p$-value $p$, \ie $\FPR = \Pr(H_0 \given p)$.
As before, $H_0$ corresponds to the point null hypothesis $H_0\colon$
$\theta = 0$. Note also that we take the exact (two-sided) $p$-value $p$ as the
observed ``data'', regardless of whether or not it is significant at some
pre-specified level, the so-called ``$p$-equals'' interpretation of NHST
\citep{Colquhoun2017}.

>>>>

Consider a null hypothesis $H_0$ with prior probability $\pi=\P(H_0)$, so
$\P(H_1) =1-\pi$ is the prior probability of the alternative hypothesis $H_1$.
Computation of the posterior probability of $H_1$ is routine with Bayes'
theorem:
\begin{equation*}
  \Pr(H_{1} \given \data) = \frac{\Pr(\data \given H_{1}) \Pr(H_{1})}{\Pr(\data \given H_{0}) \Pr(H_{0}) +
    \Pr(\data \given H_{1}) \Pr(H_{1})}.
\end{equation*}
Bayes' theorem can be written in more compact form as
\begin{equation}\label{eq4:eq0}
  \frac{\Pr(H_{1} \given \data)}{\Pr(H_{0} \given \data)} =
  \frac{\Pr(\data \given H_{1})}{\Pr(\data \given H_{0})} \,  \frac{\Pr(H_{1})}{\Pr(H_{0})},
\end{equation}
\ie{} the posterior odds are the likelihood ratio times the prior odds. The
standard 'forward-Bayes' approach thus fixes the prior odds (or one of the
underlying probabilities), determines the likelihood ratio for the available
data, and takes the product to compute the posterior odds. Of course, the latter
can be easily back-transformed to the posterior probability
$\Pr(H_{1} \given \data)$, if required. The Problem of Priors is now apparent:
in order for us to update the odds in favour of $H_1$, we must first specify the
prior odds. This can be problematic in situations where, for example, the
evidence on which to base the prior odds is controversial or even non-existent.

@@

Forward-Bayesian updating tells us how to compute the posterior precision and
mean:
\begin{align}
\label{eq4:posterior-precision}
\delta' &= \delta + \kappa, \\
\mu' &= \frac{\mu \delta + x \kappa}{\delta'}.\label{eq4:posterior-mean}
\end{align}
For example, fixed-effect (FE) meta-analysis is based on iteratively applying
\eqref{eq4:posterior-precision} and \eqref{eq4:posterior-mean} to the summary
effect estimate $x_i$ with standard error $\sigma_i$ from the $i$-th study,
$i=1,\ldots,n$, starting with an initial precision of zero. Reverse-Bayes simply
inverts these equations, which leads to the following:
\begin{align}
\label{eq4:prior-precision}
\delta &= \delta' - \kappa,  \\
\mu &= \frac{\mu'\delta' - x \kappa}{\delta}, \label{eq4:prior-mean}
\end{align}
provided $\delta' > \kappa$, \ie{} the posterior precision must be larger than the
observational precision.

@@

\subsubsection{Challenging statistically non-significant findings}
\label{sec4:nonSigAnCred}
It is also possible to challenge ``non-significant'' findings (\ie{} those for
which the CI now includes zero, so $z^2 < z_{\alpha/2}^2$) using a prior that
pushes the posterior towards being credible in the Bayesian sense, with
posterior credible interval no longer including zero, corresponding to no
effect.

@@

For illustration we consider the data from the REMAP-CAP trial that supported
the RECOVERY trial finding of decreased COVID-19 mortality from corticosteroid
use. However, this trial involved far fewer patients, and despite the point
estimate showing efficacy, the relatively large uncertainty rendered the overall
finding non-significant at the 5\% level ($\hat{\theta} = -0.34$ [95\% CI
$-0.96$ to $0.29$]). Such an outcome is frequently (and wrongly) taken to imply
no effect. The use of AnCred leads to a more nuanced conclusion. The advocacy
limit AL on the log odds ratio scale for REMAP-CAP is $-1.89$, \ie{} $0.15$ on the
odds ratio scale, see also the right plot in Figure \ref{fig4:anCredEx}. Thus
advocates of the effectiveness of corticosteroids can regard the trial as
providing credible evidence of effectiveness despite its non-significance if
external evidence supports mortality reductions (in terms of odds) in the range
0\% to 85\%. So broad an advocacy range reflects the fact that this relatively
small trial provides only modest evidential weight, and thus little constraint
on prior beliefs about the effectiveness of corticosteroids.

@@

As before, while the large study approximation may be justified in
epidemiological examples, this is less likely to be true for RCTs. In such
cases, we can adapt the approach used for sceptical priors, the size and
composition of the advocacy prior being found by setting the numbers of events
$m$ in each arm the same, but this time allowing for different numbers of
non-events in each arm via the allocation ratio $K$. The resulting variance is
then
\begin{align*}
  \tau^{2} = \frac{2}{m} + \frac{K + 1}{n}
\end{align*}
where $n$ is the number of non-events in the arm used to support the null
hypothesis (\eg{} the control arm in an RCT). With the control arm event rate
$R = m/(m + n)$ constrained to match that of the actual study, we find
\begin{eqnarray*}
  m = \frac{2 - R(1 - K)}{\tau^{2}(1 - R)} & \mbox{ and }
  &n = \frac{m(1 - R)}{R}.
\end{eqnarray*}

@@

The Problem of Priors is at its most challenging in the context of entirely
novel ``out of the blue'' effects for which no obviously relevant external
evidence exist. By their nature, such findings often attract considerable
interest both within and beyond the research community, making their reliability
of particular importance. Given the absence of external sources of evidence,
\citet{Matthews2018} proposed the concept of \emph{intrinsic
  credibility}. This requires that the evidential weight of an unprecedented
finding is sufficient to put it in conflict with the sceptical prior rendering
it non-credible. In the AnCred framework, this implies a finding possesses
intrinsic credibility at level $\alpha$ if the estimate $\hat{\theta}$ is
outside the corresponding sceptical prior interval $[-\SL, \SL]$ extracted using
Reverse-Bayes from the finding itself, \ie{} $\hat{\theta}^2 > \SL^2$ with $\SL$
given in \eqref{eq4:S}. Matthews showed this implies an unprecedented finding is
intrinsically credible at level $\alpha=0.05$ if its $p$-value does not exceed
0.013.

@@

As an example, the $p$-value for intrinsic credibility for the RECOVERY trial
finding (with $p$-value $p=0.0002$) cited earlier is $\pIC = 0.01$ and thus the
probability of the replication effect going in the same direction (\ie{} reduced
mortality in this case) is $0.995$. In contrast, the finding from the smaller
REMAP-CAP trial (with $p=0.29$) leads to $\pIC = 0.46$, and the probability of
effect direction replication is hence only $0.77$.

@@

The plausibility of the sufficiently sceptical prior can be evaluated in light
of external evidence, but what should we do in the absence of such? We could
again use the \citet{Box1980} prior-predictive check as in
Section~\ref{sec4:IC}, however, the resulting tail probability is difficult to
compare to the Bayes-factor cut-off $\gamma$. When a specific alternative model
to the null is in mind, \citet[p. 391]{Box1980} also suggested to use a Bayes
factor for model criticism of the null model. Following this approach,
\citet{Pawel2020b} proposed to define a second Bayes factor contrasting the
sufficiently sceptical prior to an optimistic prior, which they defined as
$\theta \given H_2 \sim \Nor(\hat{\theta}, \sigma^2)$ the posterior of $\theta$
based on the data and the reference prior $f(\theta) \propto 1$. The optimistic
prior therefore represents the position of a proponent who takes the original
claim at face value. This leads to the second Bayes factor being
\begin{align}
  \label{eq4:bf12}
  \BF_{12} = \sqrt{\frac{2}{1 + g}} \cdot \exp\left\{-\frac{1}{2}\cdot \frac{z^{2}}{1 + g}\right\}.
\end{align}
Analogously to the tail probability approach from Section~\ref{sec4:IC},
intrinsic credibility is established if the data support the optimistic over the
sceptical prior at a higher level than they support the sceptical prior over the
null hypothesis, \ie{} if
\begin{align*}
  \BF_{12} \leq \BF_{01}
\end{align*}
with sufficiently sceptical relative prior variance $g$ from~\eqref{ggamma} used
in both Bayes factors. For example, if we challenge the RECOVERY trial finding
such that the resulting Bayes factor is only $\BF_{01} = 1/10$, we obtain
with~\eqref{eq4:sspv} the sufficiently sceptical relative prior variance
$g = 0.59$ and in turn with~\eqref{eq4:bf12} the Bayes factor $\BF_{12} = 1/64$,
so the finding is intrinsically credible at $\gamma = 1/10$.

@@

The right plot in Figure \ref{fig4:bf} illustrates application of the procedure
on data from the meta-analysis on association between COVID-19 mortality and
corticosteroids. The coefficient of variation of the advocacy prior is fixed to
$\text{CV} = 1/z(\gamma=1/3) = 0.67$ (for comparison, the CV of the advocacy
prior in traditional AnCred at $\alpha = 0.05$ is
$\text{CV} = 1/z_{\alpha/2}= 0.51$) and thus the Bayes factor $\BF_{01}$ only
depends on the relative mean $f = \mu/\hat{\theta}$. Under the sceptical prior
only the RECOVERY finding could be challenged at $\gamma = 1/3$ (where
$z(\gamma)=1.5$ corresponds to $\alpha=13$\%). With the advocacy prior this is
now also possible for the CAPE COVID finding \citep{Dequin2020}, where a prior
with mean $\mu = f \cdot \hat{\theta} = 0.37 \cdot (-0.79) = -0.29$ and standard
deviation $\tau = \text{CV} \cdot \mu = 0.2$ is able to make the finding
compelling at $\gamma = 1/3$. The corresponding prior credible interval for the
OR at level $1-\alpha$ ranges from 0.55 to 1, so advocates may still consider
the ``non-compelling'' finding as providing moderate evidence in favour of a
benefit, if external evidence supports mortality reductions in that range. Using
the prior-to-data conversion described in
Section~\ref{sec4:prior-data-translation}, the prior can be translated to a
trial with 69 events in both arms, but 206 non-events in the treatment and 182
non-events in the control arm (such that the mortality rate in the control arm
is the same as in the CAPE-COVID trial). Note that the advocacy prior may not be
unique, \eg{} for the CAPE COVID finding the prior with relative mean
$f^\prime = 1.26$ and standard deviation $\tau^\prime = 0.67$ also renders the
data as just compelling at $\gamma = 1/3$. We recommend to choose the prior with
$f$ closer to zero, as it is the more conservative choice.

@@

Application of the Analysis of Credibility with Bayes factors as described in
Section \ref{sec4:bfs} assumes some familiarity with Bayes factors as measures
of evidence. \citet{Colquhoun2019} argued that very few nonprofessional users of
statistics are familiar with the notion of Bayes factors or likelihood ratios.
He proposes to quantify evidence with the \emph{false positive risk}, ``if only
because that is what most users still think, mistakenly, that that is what the
$p$-value tells them''. More specifically, \citet{Colquhoun2019} defines the
\FPR{} as the posterior probability that the point null hypothesis $H_0$ of no
effect is true given the observed $p$-value $p$, \ie{} $\FPR = \Pr(H_0 \given p)$.
As before, $H_0$ corresponds to the point null hypothesis $H_0\colon$
$\theta = 0$. Note also that we take the exact (two-sided) $p$-value $p$ as the
observed ``data'', regardless of whether or not it is significant at some
pre-specified level, the so-called ``$p$-equals'' interpretation of NHST
\citep{Colquhoun2017}.

### 2022-11-30 paper5.tex
ie and eg

The BAE ``tipping point'' is then defined as the least extreme prior mean that
results in a posterior credible interval which excludes the null value. If the
substantive hypothesis is for positive effect estimates (\eg
$\log(\mbox{HR}) > 0$) the BAE is the prior mean which leads to the lower limit
$L_{p}$ of the $100(1 - \alpha)$\% posterior credible interval being zero
\begin{align}
  L_{p} = \mu_{p} - z_{\scriptscriptstyle \alpha/2} \, \tau_{p} = 0
  \label{eq5:postcredL}
\end{align}
while for negative effect estimates the upper limit $U_{p}$ is fixed to zero
\begin{align}
  U_{p} = \mu_{p} + z_{\scriptscriptstyle \alpha/2} \, \tau_{p} = 0
  \label{eq5:postcredU}
\end{align}
with $z_{\scriptscriptstyle \alpha/2}$ the $1 - \alpha/2$ quantile of the
standard normal distribution. Combining Eq.~\eqref{eq5:varconstraints} with
Eq.~\eqref{eq5:postcredL}, respectively Eq.~\eqref{eq5:postcredU}, leads to
\begin{align}
  \text{BAE}
  & =  \sign(\hat{\theta}) \sqrt{2} \, z_{\scriptscriptstyle \alpha/2} \, \sigma - \hat{\theta}
    \label{eq5:bae}
\end{align}
where $\sign(\hat{\theta}) = 1$ when $\hat{\theta} > 0$ and
$\sign(\hat{\theta}) = -1$ otherwise. Re-written in terms of the upper and lower
$100(1 - \alpha)$\% confidence interval (CI) limits $U$ and $L$ of the effect
estimate $\hat{\theta}$ we obtain
\begin{align}
  \text{BAE} = \frac{\text{sign}(\hat{\theta}) \sqrt{2} (U - L) - (U + L)}{2}
  \label{eq5:baeneg}
\end{align}
We see from Eq.~\eqref{eq5:bae} that Sondhi et al.'s proposal has the intuitive
property that as the study becomes more convincing (through larger effect sizes
$|\hat{\theta}|$ and/or smaller standard errors $\sigma$), the BAE will decrease
(increase) for positive (negative) $\hat{\theta}$, indicating that less
additional evidence is needed to push a non-significant study towards
credibility. Eq.~\eqref{eq5:bae} and Eq.~\eqref{eq5:baeneg} also hold for
significant studies but the BAE then represents the mean of a ``sceptical''
prior which renders the study non-significant.

@@

Thus additional evidence in the form of prior insight or a subsequent
replication supporting an HR at least as impressive as this (\ie an
$\mbox{HR} < 0.52$ in this case), and a CI at least as tight as that of the
original study will render this non-significant result credible at the 95\%
level. Sondhi et al. cite prior evidence from \citet{Innocenti2019} who found an
$\mbox{HR} = 0.13$ (95\% CI: 0.06 to 0.30) which meets both criteria set by the
BAE, and renders the original study credible.

@@

\section{Alternatives approaches}
In order to get a unique solution for the BAE, Sondhi et al. make the assumption
that the prior variance equals the data variance, but also other possibilities
exist. An alternative rationale would be to set the mean of the additional
evidence, rather than variance, to that of the original finding (\ie
$\mu = \hat{\theta}$), and determining the prior variance $\tau^{2}$ such that
the posterior credible interval includes the null value. Under this approach,
the prior variance is given by
\begin{align*}
  \tau^{2} = \frac{\sigma^{2}}{z_{\scriptscriptstyle \alpha/2}^2/z^2 - 1}
\end{align*}
with $z = \hat{\theta}/\sigma$. The resulting prior represents a study with
identical effect estimate but different precision compared to the observed one.
As the observed study becomes more convincing (with larger effect estimates
$|\hat{\theta}|$ and/or smaller standard errors $\sigma$), the prior will become
more diffuse, so less additional evidence is needed to render the finding
credible. We see in Figure~\ref{fig5:illustration} that prior and posterior are
similar to BAE for the clinical trial data from Sondhi et al.

>>>>

The BAE ``tipping point'' is then defined as the least extreme prior mean that
results in a posterior credible interval which excludes the null value. If the
substantive hypothesis is for positive effect estimates (\eg{}
$\log(\mbox{HR}) > 0$) the BAE is the prior mean which leads to the lower limit
$L_{p}$ of the $100(1 - \alpha)$\% posterior credible interval being zero
\begin{align}
  L_{p} = \mu_{p} - z_{\scriptscriptstyle \alpha/2} \, \tau_{p} = 0
  \label{eq5:postcredL}
\end{align}
while for negative effect estimates the upper limit $U_{p}$ is fixed to zero
\begin{align}
  U_{p} = \mu_{p} + z_{\scriptscriptstyle \alpha/2} \, \tau_{p} = 0
  \label{eq5:postcredU}
\end{align}
with $z_{\scriptscriptstyle \alpha/2}$ the $1 - \alpha/2$ quantile of the
standard normal distribution. Combining Eq.~\eqref{eq5:varconstraints} with
Eq.~\eqref{eq5:postcredL}, respectively Eq.~\eqref{eq5:postcredU}, leads to
\begin{align}
  \text{BAE}
  & =  \sign(\hat{\theta}) \sqrt{2} \, z_{\scriptscriptstyle \alpha/2} \, \sigma - \hat{\theta}
    \label{eq5:bae}
\end{align}
where $\sign(\hat{\theta}) = 1$ when $\hat{\theta} > 0$ and
$\sign(\hat{\theta}) = -1$ otherwise. Re-written in terms of the upper and lower
$100(1 - \alpha)$\% confidence interval (CI) limits $U$ and $L$ of the effect
estimate $\hat{\theta}$ we obtain
\begin{align}
  \text{BAE} = \frac{\text{sign}(\hat{\theta}) \sqrt{2} (U - L) - (U + L)}{2}
  \label{eq5:baeneg}
\end{align}
We see from Eq.~\eqref{eq5:bae} that Sondhi et al.'s proposal has the intuitive
property that as the study becomes more convincing (through larger effect sizes
$|\hat{\theta}|$ and/or smaller standard errors $\sigma$), the BAE will decrease
(increase) for positive (negative) $\hat{\theta}$, indicating that less
additional evidence is needed to push a non-significant study towards
credibility. Eq.~\eqref{eq5:bae} and Eq.~\eqref{eq5:baeneg} also hold for
significant studies but the BAE then represents the mean of a ``sceptical''
prior which renders the study non-significant.

@@

Thus additional evidence in the form of prior insight or a subsequent
replication supporting an HR at least as impressive as this (\ie{} an
$\mbox{HR} < 0.52$ in this case), and a CI at least as tight as that of the
original study will render this non-significant result credible at the 95\%
level. Sondhi et al. cite prior evidence from \citet{Innocenti2019} who found an
$\mbox{HR} = 0.13$ (95\% CI: 0.06 to 0.30) which meets both criteria set by the
BAE, and renders the original study credible.

@@

\section{Alternatives approaches}
In order to get a unique solution for the BAE, Sondhi et al. make the assumption
that the prior variance equals the data variance, but also other possibilities
exist. An alternative rationale would be to set the mean of the additional
evidence, rather than variance, to that of the original finding (\ie{}
$\mu = \hat{\theta}$), and determining the prior variance $\tau^{2}$ such that
the posterior credible interval includes the null value. Under this approach,
the prior variance is given by
\begin{align*}
  \tau^{2} = \frac{\sigma^{2}}{z_{\scriptscriptstyle \alpha/2}^2/z^2 - 1}
\end{align*}
with $z = \hat{\theta}/\sigma$. The resulting prior represents a study with
identical effect estimate but different precision compared to the observed one.
As the observed study becomes more convincing (with larger effect estimates
$|\hat{\theta}|$ and/or smaller standard errors $\sigma$), the prior will become
more diffuse, so less additional evidence is needed to render the finding
credible. We see in Figure~\ref{fig5:illustration} that prior and posterior are
similar to BAE for the clinical trial data from Sondhi et al.
